\pkg{cv}: An \proglang{R} Package for Cross-Validating Regression Models

### 2024-07-14 scratch/notes_john/JSS-article/JSS-article-4.Rmd
finish replacing ` ` with \code{ } in JSS-article-4

We check first whether the default \code{cv()} method works "out-of-the-box" for the \code{"multinom"} model:
```{r BEPS-test-default, error=TRUE}
cv(m.beps, seed = 3465, criterion = BayesRuleMulti)
```
The default method of \code{GetResponse()} (a function supplied by the \pkg{cv} package---see \code{?GetResponse}) fails for a \code{"multinom"} object. A straightforward solution is to supply a \code{GetResponse.multinom()} method that returns the factor response [using the `get_response()` function from the \pkg{insight} package, @LudeckeWaggonerMakowski:2019],
```{r GetResponse.multinom}
GetResponse.multinom <- function(model, ...) {
  insight::get_response(model)
}

>>>>

We check first whether the default \code{cv()} method works "out-of-the-box" for the \code{"multinom"} model:
```{r BEPS-test-default, error=TRUE}
cv(m.beps, seed = 3465, criterion = BayesRuleMulti)
```
The default method of \code{GetResponse()} (a function supplied by the \pkg{cv} package---see \code{?GetResponse}) fails for a \code{"multinom"} object. A straightforward solution is to supply a \code{GetResponse.multinom()} method that returns the factor response [using the \code{get\_response()} function from the \pkg{insight} package, @LudeckeWaggonerMakowski:2019],
```{r GetResponse.multinom}
GetResponse.multinom <- function(model, ...) {
  insight::get_response(model)
}
